---
title: "Mini Project 3: Accessible Camping!"
author: "Cassie Naranjo and Amelia Stapleton"
date: "4/15/2019"
output: 
  html_document:
    code_folding: hide
---
**Introduction:**
Have you ever wanted to go the Macleish Station and enjoy a campsite with friends or on your own, but don't actually want to hike the distance to the campsite? Or perhaps you are physically unable to hike to one of the already resurrected campsites? Well, we have a solution for you! We have used spatial data of the Macleish Field Station to discover two new potential campsite locations that are easily accessible from the main parking lot or Conway Road. Both of these proposed campsites follow the guidelines of: less than 0.5 miles away from the parking lot, 200 feet away from a stream or other body of water, more than 500 feet away from a challenge course or research area, relatively flat, within the boundraries of Macleish, and positioned in vegetation that is unlike the two campsites that already exist, the group campsite and the remote campsite.

```{r,include = FALSE, echo = FALSE}
library(tidyverse)
library(sf)
library(macleish)
library(leaflet)
```
*Determing the location of the parking lot*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

parking <- data.frame(lat = 42.448013, lon = -72.68066)
parking_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = parking,
             popup = "Parking Lot")
parking_plot
```
*Determing the location of the group campsite*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

group_campsite <- data.frame(lat = 42.450976, lon = -72.678154)
group_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite,
             popup = "Group Campsite")
group_plot
```
*Determining the location of the remote campsite*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

remote_campsite <- data.frame(lat = 42.458549, lon = -72.679581)
remote_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = remote_campsite,
             popup = "Remote Campsite")
remote_plot
```
*Combining the 3 sites (parking, remote campsite, and group campsite) into one map*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

base_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite,
             popup = "Group Campsite") %>%
  addMarkers(lng = ~lon, lat = ~lat, data = remote_campsite,
             popup = "Remote Campsite") %>%
  addMarkers(lng = ~lon, lat = ~lat, data = parking,
             popup = "Parking Lot") 
  base_plot
```
*Determing the Macleisch Station boundary*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

boundary <- macleish_layers %>% 
pluck("boundary")

base_plot %>%
addPolygons(data = boundary, color = "black")
```
*Determing the locations of the streams and wetlands*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

leaflet() %>%
addTiles %>% 
addPolygons(data = pluck(macleish_layers, "wetlands"), color = ~SHAPE_AREA, popup = ~IT_VALDESC) %>%
addPolylines(data = pluck(macleish_layers, "streams"), weight = 3, color = "orange")
```
*Adding a buffer the streams to ensure proposed campsites are within 200 feet of a body of water*
```{r, message = FALSE, warning = FALSE, results = 'hide'}
#Adding a buffer the streams to ensure proposed campsites are within 200 feet of a body of water

proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

buffer_streams <- macleish_layers %>%
  pluck("streams") %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 60.96) %>%
  st_transform(4326)

leaflet() %>%
  addTiles %>% 
  addPolygons(data = buffer_streams)
```
*Looking at the different forest types within Macleish to ensure our new campsites are in a different vegetation zone than previous campsites*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

forest_pal <- colorFactor("plasma", 
macleish_layers %>%
pluck("forests") %>%
pull(VegType_21)
)

leaflet() %>%
addTiles %>% 
addPolygons(data = pluck(macleish_layers, "forests"), color = ~forest_pal(VegType_21), fillOpacity = 0.8, weight = 0.1, popup = ~Sheet1__Na)
```
*Viewing the contours of Macleish to assess potential campsite locations and ensure they are housed on relatively flat land, using the 3m contour dataset because it is more detailed compared to the 30 ft dataset*
```{r,message = FALSE, warning = FALSE, results = 'hide'}

leaflet() %>%
addTiles() %>%
addPolylines(data = pluck(macleish_layers, "contours_3m"), weight = 1, color = "red") 
```
*Determing the location of the challenge courses to allow for 500 feet between any of these locations and our proposed campsites*
```{r, message = FALSE, warning = FALSE, results = 'hide'}

challenge_area <- leaflet() %>%
addTiles %>% 
addCircles(data = pluck(macleish_layers, "challenge_courses"))

buffer_challenge <- macleish_layers %>%
  pluck("challenge_courses") %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

leaflet() %>%
  addTiles %>% 
  addPolygons(data = buffer_challenge, weight = 1, color = "red")
```
*Determing the location of the research areas to allow for 500 feet between any of these locations and our proposed campsites*
```{r, message = FALSE, warning = FALSE,results = 'hide'}

leaflet() %>%
  addTiles() %>%
  addPolygons(data = pluck(macleish_layers, "research"), color = "yellow")

buffer_research <- macleish_layers %>%
  pluck("research") %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

leaflet() %>%
  addTiles %>% 
  addPolygons(data = buffer_research, weight = 1, color = "yellow")

```
*The choosen coordinates for new campsites, found by trial and error*
```{r, message = FALSE, warning = FALSE}

BlackBirch_campsite <- data.frame(lat = 42.44788, lon = -72.680015)
RedOak_campsite <- data.frame(lat = 42.45425, lon = -72.68540)
```

*Code for making cool icons*

```{r, message = FALSE, warning = FALSE}

campicon <- makeIcon(
  iconUrl = "http://icons.iconarchive.com/icons/thegirltyler/brand-camp/256/Camp-Fire-Stories-icon.png",
  iconWidth = 25, iconHeight = 30)
```
**The final map with our proposed campsites and all the criteria that went into determining these locations:**
```{r, message = FALSE, warning = FALSE}
leaflet() %>%
addTiles() %>%
addMarkers(lng = ~lon, lat = ~lat, data = group_campsite,popup = "Group Campsite") %>%
addMarkers(lng = ~lon, lat = ~lat, data = remote_campsite,popup = "Remote Campsite") %>%
addMarkers(lng = ~lon, lat = ~lat, data = parking,popup = "Parking Lot") %>%
addMarkers(lng = ~lon, lat = ~lat, data = BlackBirch_campsite,
             popup = "New Campsite #1", icon = campicon) %>%
addMarkers(lng = ~lon, lat = ~lat, data = RedOak_campsite, popup = "New Campsite #2", icon = campicon) %>%
addCircles(data = parking, radius = 804, color = "grey") %>%
addPolygons(data = boundary, color = "black") %>%
addPolygons(data = pluck(macleish_layers, "wetlands"), color = ~SHAPE_AREA, popup = ~IT_VALDESC) %>%
addPolylines(data = pluck(macleish_layers, "streams"), weight = 7, color = "navy") %>%
addPolylines(data = pluck(macleish_layers, "contours_3m"), weight = 1, color = "red") %>%
addPolygons(data = pluck(macleish_layers, "research"), color = "yellow") %>%
addCircles(data = pluck(macleish_layers, "challenge_courses"), fillOpacity = 1) %>%
addPolygons(data = pluck(macleish_layers, "forests"), color = ~forest_pal(VegType_21), fillOpacity = 0.5, weight = 0.1, popup = ~Sheet1__Na) %>%
addPolylines(data = pluck(macleish_layers, "trails"), weight = 3, color = "black")
```
*The final map showing the buffers for streams (less than 200 feet from) and research areas/challenge courses (500 feet away):*
```{r}
leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = BlackBirch_campsite,
             popup = "New Campsite #1", icon = campicon) %>%
addMarkers(lng = ~lon, lat = ~lat, data = RedOak_campsite, popup = "New Campsite #2", icon = campicon) %>%
  addPolygons(data = buffer_streams) %>%
  addPolygons(data = buffer_challenge, weight = 1, color = "red") %>%
  addPolygons(data = buffer_research, weight = 1, color = "yellow")
```

*Discussion:*
When looking at the group and remote campsites that already exist, they are situated in Old Field White Pine Forest and Sugar Maple Forest, respectively. The campsites that we are suggesting, New Campsite #1 and New Campsite #2, are located in Old Pasture Black Birch Forest and Red Oak Forest, respectively. These two campsites abide by the set criteria, other than the New Campsite #2, the Red Oak Campsite, being right on the cusp of the 500 feet border of a research area. After talking to Paul Wetzel and showing him our proposed plan, he pointed out a few things. First, New Campsite #2 is relativly close to Conway Road. Although this not necessarily a bad thing, we do feel it's an important think for potential campers to be aware of. Second, he pointed out that the location of New Campsite #1 is heavily populated by rose bushes. Although beautiful at some point of the year, this may pose an annoyance to campers due to their thorns and may required regular maintenance. 

+1 for including relevant external information in your analysis
what will it cost?
+1 for reporting at least one actionable recommendation (what should Smith DO with your findings?)
how long will it take?
*Resources Necessary:*
In order to make these two new campsites inhabitable for future campers, a wide enough area for a tent, a few chairs, and maybe a fire pit would need to be cleared. This may include needing to chop down and unearth some trees and clearing branches for enough overhead space. Additionally, it may be necessary to build an in-ground fire pit for both warmth and cooking. Chairs and seating arrangements could be built from the chopped down trees or from rocks around the area. 
Regular maintenance including but not limited to branch/vegetation clearing, trash clean up, and raking would need to occur. 
We believe that the enviromental impact of this campsite will be minor as long as the resources used to build the campsite itself are sustainable, the folks using the campsite are enviromentally conscious and clean up after themselves, and only approved wood and/or materials are burnt in the firepit. 
do you see  major roadblocks?

Footnotes:
Github repository link
Issues post

Notes for Write-Up:
Stream doesn't always flow 
close to a road 
other one is full of roses that creates umbrella of rose bushes 

*Word Count*
```{r, message = FALSE, echo = FALSE}
##Word Count
wordcountaddin::word_count()
```