---
title: "MP3"
author: "Cassie Naranjo"
date: "4/12/2019"
output:
    html_document:
    code_folding: hide
=======
author: "Cassie Naranjo and Amelia Stapleton"
date: "4/15/2019"
output: 
  html_document:
  code_folding: show

---
To do:
+1 unnecessary messages from R are hidden from being displayed in the HTML
+1 for using code folding to keep your code hidden, but still make it available.
+1 for including a problem statement (what are you trying to figure out?)
+1 for readable, well-documented code (i.e. appropriate comments, using line breaks, breaking code up into logical chunks) that conforms to a style guide
+1 for including a catchy and/or engaging title
+1 for having at least 500 words and no more than 800 words
+1 for including relevant external information in your analysis
+1 for reporting at least one actionable recommendation (what should Smith DO with your findings?)
+1 for using a GitHub repository and including a link to it in the footnotes
+1 for using the Issues tab on GitHub to plan your project
+1 for including a short discussion on the resources necessary to implement your recommendation:
what will it cost?
how long will it take?
are there any concerns about environmental impact?
do you see any major roadblocks?
+0–2 reflects the professor’s judgment of the overall quality of your submission
0: graphics are relatively simple, confusing, sloppily executed, or not well thought out; analysis is muddled or uninformed
1: a solid all-around effort, graphics are appropriate, labeled, and contextualized; analysis is reasonable, considered, and well-researched
2: graphics are special, showing creativity, an original design, and/or exceptional attention to detail; analysis is exceptionally thorough and well thought out

```{r,include = FALSE, echo = FALSE}
library(tidyverse)
library(sf)
library(macleish)
library(leaflet)
```
Location of Parking Lot 
```{r, message = FALSE, warning = FALSE}
parking <- data.frame(lat = 42.448013, lon = -72.68066)
base_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = parking,
             popup = "Parking Lot")
base_plot
```
Location of Group Campsite 
```{r, message = FALSE, warning = FALSE}
group_campsite <- data.frame(lat = 42.450976, lon = -72.678154)
base_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite,
             popup = "Group Campsite")
base_plot
```
Location of Remote Campsite
```{r, message = FALSE, warning = FALSE}
remote_campsite <- data.frame(lat = 42.458549, lon = -72.679581)
base_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = remote_campsite,
             popup = "Remote Campsite")
base_plot
```

Plot of all 3 sites 
```{r, message = FALSE, warning = FALSE}
base_plot <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite,
             popup = "Group Campsite") %>%
  addMarkers(lng = ~lon, lat = ~lat, data = remote_campsite,
             popup = "Remote Campsite") %>%
  addMarkers(lng = ~lon, lat = ~lat, data = parking,
             popup = "Parking Lot") 
  base_plot
```

Plotting boundary
```{r, message = FALSE, warning = FALSE}
boundary <- macleish_layers %>% 
pluck("boundary")

base_plot %>%
addPolygons(data = boundary, color = "black")
```
Looking at the locations of streams and other water sources:
```{r, message = FALSE, warning = FALSE}
leaflet() %>%
addTiles %>% 
addPolygons(data = pluck(macleish_layers, "wetlands"), color = ~SHAPE_AREA, popup = ~IT_VALDESC) %>%
addPolylines(data = pluck(macleish_layers, "streams"), weight = 3, color = "orange")
```

```{r, message = FALSE, warning = FALSE}
macleish_layers %>%
pluck("streams") %>%
st_buffer(dist = .1)
```
Not sure how to make a buffer around the streams using leaflet...


Looking at forest types...Tells us where the different forest types are but not what each one represents color wise. Maybe if we could add a legend to know what the colors represent?


Looking at forest types:
Naming the color palette:
```{r, message = FALSE, warning = FALSE}
forest_pal <- colorFactor("plasma", 
macleish_layers %>%
pluck("forests") %>%
pull(VegType_21)
)
```
Outlining the different forests:
```{r, message = FALSE, warning = FALSE}
leaflet() %>%
addTiles %>% 
addPolygons(data = pluck(macleish_layers, "forests"), color = ~forest_pal(VegType_21), fillOpacity = 0.8, weight = 0.1, popup = ~Sheet1__Na)
```
Contours:
Using the 3m contours because much more detailed compared to the 30 ft
```{r,message = FALSE, warning = FALSE}
leaflet() %>%
addTiles() %>%
addPolylines(data = pluck(macleish_layers, "contours_3m"), weight = 1, color = "red") 
```
Adding contours to parking, campsites, streams/wetlands, and contour maps:
```{r, message = FALSE, warning = FALSE}
leaflet() %>%
addTiles() %>%
addMarkers(lng = ~lon, lat = ~lat, data = group_campsite,popup = "Group Campsite") %>%
addMarkers(lng = ~lon, lat = ~lat, data = remote_campsite,popup = "Remote Campsite") %>%
addMarkers(lng = ~lon, lat = ~lat, data = parking,popup = "Parking Lot") %>%
addCircleMarkers(data = parking, color = "black", radius = 804) %>%
addPolygons(data = pluck(macleish_layers, "wetlands"), color = ~SHAPE_AREA, popup = ~IT_VALDESC) %>%
addPolylines(data = pluck(macleish_layers, "streams"), weight = 3, color = "orange") %>%
addPolylines(data = pluck(macleish_layers, "contours_3m"), weight = 1, color = "red")
```
Challenge Courses
```{r, echo = FALSE}
challenge_area <- leaflet() %>%
addTiles %>% 
addCircles(data = pluck(macleish_layers, "challenge_courses"))
```
Coordinates for new campsites
```{r, message = FALSE, warning = FALSE}
BlackBirch_campsite <- data.frame(lat = 42.44788, lon = -72.680015)
RedOak_campsite <- data.frame(lat = 42.45425, lon = -72.68540)
```
Making cool icons: 
```{r, message = FALSE, warning = FALSE}
campicon <- makeIcon(
  iconUrl = "http://icons.iconarchive.com/icons/thegirltyler/brand-camp/256/Camp-Fire-Stories-icon.png",
  iconWidth = 25, iconHeight = 30)
```
Adding to other maps:
```{r, message = FALSE, warning = FALSE}
leaflet() %>%
addTiles() %>%
addMarkers(lng = ~lon, lat = ~lat, data = group_campsite,popup = "Group Campsite") %>%
addMarkers(lng = ~lon, lat = ~lat, data = remote_campsite,popup = "Remote Campsite") %>%
addMarkers(lng = ~lon, lat = ~lat, data = parking,popup = "Parking Lot") %>%
addMarkers(lng = ~lon, lat = ~lat, data = BlackBirch_campsite,
             popup = "New Campsite #1", icon = campicon) %>%
addMarkers(lng = ~lon, lat = ~lat, data = RedOak_campsite, popup = "New Campsite #2", icon = campicon) %>%
addCircles(data = parking, radius = 804, color = "grey") %>%
addPolygons(data = boundary, color = "black") %>%
addPolygons(data = pluck(macleish_layers, "wetlands"), color = ~SHAPE_AREA, popup = ~IT_VALDESC) %>%
addPolylines(data = pluck(macleish_layers, "streams"), weight = 7, color = "navy") %>%
addPolylines(data = pluck(macleish_layers, "contours_3m"), weight = 1, color = "red") %>%
addPolygons(data = pluck(macleish_layers, "research"), color = "yellow") %>%
addCircles(data = pluck(macleish_layers, "challenge_courses"), fillOpacity = 1) %>%
addPolygons(data = pluck(macleish_layers, "forests"), color = ~forest_pal(VegType_21), fillOpacity = 0.5, weight = 0.1, popup = ~Sheet1__Na) %>%
addPolylines(data = pluck(macleish_layers, "trails"), weight = 3, color = "black")
```

Stream doesn't always flow 
close to a road 
other one is full of roses that creates umbrella of rose bushes 
